Over-relaxed Sinkhorn's Algorithm for Regularized Optimal Transport

### 2017-10-10 paper.tex
Suite corrections

\begin{proof}[Proof of the theorem]
	(New proof, using the Lyapunov function. Much shorter and cleaner than the one from my report.)
	First of all, notice that the operators $P_{\Ccal_k}^\theta$ apply a scaling to lines or columns of matrices. All $(\gamma^l)$ are thus diagonally similar to $\gamma^0$:
	\[
	\forall l\ge0,\quad \gamma^l \in S
	\]

>>>>

\begin{proof}[Proof of the theorem]
	First of all, notice that the operators $P_{\Ccal_k}^\theta$ apply a scaling to lines or columns of matrices. All $(\gamma^l)$ are thus diagonally similar to $\gamma^0$:
	\[
	\forall l\ge0,\quad \gamma^l \in S
	\]
